Bayesian estimation of chronic disease epidemiology from incomplete data

### 2021-10-02 metahit/paper_analyses.Rmd
Clean up

Fuck me the Rhats are fucked 
Theyve basically all broken . 
Must be some unused parameter or wev that has been left in to break it 
Use the optim models to debug it 
looks like the incidence related parameters
beta_inc not in tidy but can't tell

@@

resg <- resg %>% filter(disease != "Stomach cancer") # only national estimates
# convergence check
summary(resg$Rhat)  # 
resnc <- resg %>% filter(Rhat > 2) 
resnc <- resg %>% filter(Rhat > 1.1) 
resnc <- resg %>% filter(Rhat > 1.01)

resnc <- resg %>% filter(Rhat > 1.1, disease=="Ischemic heart disease") 
resg %>% filter(grepl("beta_inc",var))

table(resnc$disease)
table(resnc$disease, resnc$area)

>>>>

@@

resg <- resg %>% filter(disease != "Stomach cancer") # only national estimates
# convergence check
summary(resg$Rhat)  # 
resnc <- resg %>% filter(Rhat > 2) 
resnc <- resg %>% filter(Rhat > 1.1) 
resnc <- resg %>% filter(Rhat > 1.01) 
table(resnc$disease)
table(resnc$disease, resnc$area)
